Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-10 CJM/letter to CJM.tex
letter

\begin{enumerate}
\item[(i)] Thank you for noticing this. We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$. To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients. 
\item[(ii)] Thank you for pointing this out. We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field. 
\item[(iii)] We fixed this typo.
\item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
\item[(v)] We replaced every instance of $S$ with $\Spec(R)$, which is what we meant by $S$, though we had neglected to say that anywhere.
\item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper. We have also given a precise citation to Yu's paper showing where the "recursive definition" can be found.
\item[(vii)] Fixed this typo.
\end{enumerate}

>>>>

\begin{enumerate}
\item[(i)] Thank you for noticing this. We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$. To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients. 
\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field. 
\item[(iii)] We fixed this typo.
\item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
\item[(v)] We replaced every instance of $S$ with $\Spec(R)$, which is what we meant by $S$, though we had neglected to say that anywhere.
\item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper. We have also given a precise citation to Yu's paper showing where the "recursive definition" can be found.
\item[(vii)] Fixed this typo.
\end{enumerate}
